---
title: "Add Code Eligibility Coding Exercise"
format: html
editor: visual
---

## Instructions

Run the following code chunks and complete all necessary prompts with your own code. Once finished, follow the submission instructions on the Github Repository's README.

## Setup

```{r load-packages}
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(dplyr)
```

## Data Exploration

Run the following code cell to explore the data a bit.

```{r data-exploration}


# Create palmer penguins dataframe
penguins_df <- penguins
# Examine the structure of the dataset
str(penguins_df)
glimpse(penguins_df)

# Generate summary statistics
summary(penguins_df)

```

## Data Cleaning

Complete the following data cleaning steps in the `penguins_df` dataframe:

1.  Remove observations with missing values
2.  Create a new column in `penguins_df`called `length_mass` that measures the length to mass ratio of each penguin.

```{r data-cleaning}

# Remove missing values
penguins_df <- penguins_df |>
  drop_na()


# Create length_mass column that measures length to mass ratio for each penguin
penguins_df <- penguins_df |>
  mutate(length_mass = flipper_length_mm / body_mass_g)
```

## Data Visualization

Use `ggplot` to make a visualization of your choice with the penguin data. Be sure you include the following in your visualization:

-   An updated title

-   Updated axis labels

-   A color palette/ colors of your choosing (not default ggplot colors)

-   Comments!

```{r data-viz}
ggplot(penguins_df, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point(size = 2) +
  # Add in the title and axis labels
  labs(
    title = "Penguin Flipper Length vs Body Mass",
    x = "Flipper Length (mm)",
    y = "Body Mass (g)"
  ) +
  # Create a custom color palette for species
  scale_color_manual(values = c("Adelie" = "darkseagreen3", "Chinstrap" = "darkslategray", "Gentoo" = "darkturquoise")) +
  # Use a classic theme for the plot
  theme_classic() +
  # Take out the legend title
  theme(legend.title = element_blank()) +
  geom_smooth(method = "lm", se = FALSE, color = "black") # Adding a linear model line
```

That's it! Head back to the README on the Github repo for submission instructions.
